---
title: "Data605_Assignment5"
author: "Ritesh Lohiya"
date: "September 28, 2018"
output: html_document
---

#                             ASSIGNMENT 5

#           IS 605 FUNDAMENTALS OF COMPUTATIONAL MATHEMATICS

Choose independently two numbers B and C at random from the interval [0, 1] with uniform density. Prove that B and C are proper probability distributions. Note that the point (B,C) is then chosen at random in the unit square.

B and C are proper probabilty distrubution if both B and C have a 100% chance of falling in between [0,1]  and B+C combined have a 100% chance of falling between [0,2].

```{r}
#Randomly select 10000 numbers between 0 and 1
B <- runif(10000, min = 0, max =1)
head(B)
tail(B)
```

```{r}
#Randomly select 10000 numbers between 0 and 1
C <- runif(10000, min = 0, max =1)
head(C)
tail(C)
```

```{r}
head(B+C)
tail(B+C)
```


Find the probability that

(a) B + C < 1/2.

```{r}
a <- sum((B+C) < .5)/10000
print(paste("The probability that B+C will be less than 1/2 is",a))
```


(b) BC < 1/2.

```{r}
b <- (sum((B*C) < .5)/10000)
print(paste("The probability that B*C will be less than 1/2 is",b))
```

(c) |B ??? C| < 1/2.

```{r}
c <- sum(abs((B-C)) < .5)/10000
print(paste("The probability that |B-C| will be less than 1/2 is",c))
```

(d) max{B,C} < 1/2.

```{r}
t <- 0
for(i in 1:10000){
  if(max(c(B[i],C[i])) < 0.5){
    t = t+1
  }
}
d <- t/10000
print(paste("The probability that max{B,C} will be less than 1/2 is",d))
```

(e) min{B,C} < 1/2.

```{r}
t <- 0
for(i in 1:10000){
  if(min(c(B[i],C[i])) < 0.5){
    t = t+1
  }
}
e <- t/10000
print(paste("The probability that min{B,C} will be less than 1/2 is",e))
```


